---
title: "R Notebook"
output: 
  html_notebook: 
    fig_height: 3
    fig_width: 4.5
---

```{r setup, include=FALSE}
load("sims.RData")
library(ggplot2)
```

Here's a glimpse of the raw data:

```{r}
head(sims)
```

`repetition` is just the number of the simulation of a particular set of parameters, from 1-10. The next six columns
are parameters: 
* `b` is the benefit of being helped; the cost was always 1.
* `periods` is the number of periods in a generation.
* `memory` is the length of GR types' memory.
  - This was implemented as follows: individuals just remembered the last `memory` periods (not the last `memory` times
they met somebody). For technical reasons that made things much quicker. 
* `G` is number of groups.
* `N` is total population. 

The simulation stopped when one strategy had 0.99 of the population (`fixation_threshold`).

The next columns are results. 
* `generation` says when the simulation stopped. 
* `winner` is which strategy went to fixation, GR or S.
* `cor_prop_fit` is the correlation between group fitness, and the proportion of GR types.
* `cor_prop_reput` is the correlation between group reputation, and the proportion of GR types.
* `cor_reput_fit` is the correlation between group reputation, and group fitness.

The last three are averages over all generations (taken at the last period).

The data is also in the CSV file "sims.csv".

# Basic facts

Here's the parameters that were used:

```{r}
apply(sims[2:6], 2, unique)
```



Selfish strategies mostly won:
```{r}
barplot(table(sims$winner), ylab = "Num wins")
```

# Comparative statics

These graphs show the proportion of GR wins, for values of each individual parameter.

```{r}
show_wins <- function(param) {
  tbl <- table(sims$winner, sims[[param]], dnn = c("Winner", param)) %>% prop.table(2)
  print(round(tbl, 2))
  barplot(tbl[1,], col = c("blue"), ylab = "Proportion of GR wins", xlab = param)
}
show_wins("b")
show_wins("periods")
show_wins("memory")
show_wins("G")
show_wins("N")
```

Results are much as expected. Higher b, smaller groups, smaller population all lead to more GR wins. Number of periods seems not to matter much; oddly, long memory seems to have made things worse for GR.

Why does population matter? One reason could be more groups. This might mean GR guys spend more time meeting new 
groups and perhaps getting suckered. If so the effect should be less when there are more periods. But there's not much evidence for that:

```{r}
table(sims$winner, interaction(sims$N, sims$periods)) %>% prop.table(2) %>% barplot(legend.text = c("GR", "S"))
```

The next plot shows average wins out of 10 for all of the 32 conditions.

```{r}
sims %>% 
      group_by(b, periods, memory, G, N) %>% 
      summarize(GR_wins = mean(winner == "GR")) %>% 
      mutate(
        label = sprintf("b %s, pds %s, mem %s, G %s, N %s", b, periods, memory, G, N)
      ) -> summaries

# par(mar = c(5, 10, 1, 1))
# barplot(summaries$GR_wins, names.arg = summaries$label, horiz = TRUE, cex.names = .6, las = 2, border = NA, col = "blue")

ggplot(summaries, aes(y = GR_wins, x = factor(b), colour = factor(periods), shape = factor(memory))) + geom_point(alpha = .5, position = position_jitter(width = 0.1, height = 0)) + facet_grid(G ~ N, labeller = "label_both") + xlab("b")
```


# Mechanisms

We'll plot those last three correlations against which group won. 

```{r}
f <- function(ggobj, var) {
  ggobj + 
        geom_violin(aes_string(y = var)) + 
        geom_point(aes_string(y = var), alpha = .2, color = 'brown', position = position_jitter(width = .05, 
          height = 0))
}

p <- ggplot(sims, aes(x = winner))
f(p, "cor_prop_fit")
f(p, "cor_prop_reput")
f(p, "cor_reput_fit")
```

So, overall, when GR types win,  these correlations are high. `cor_prop_reput` seems to have two groups, not sure why. 

Lastly, you can see how long things took to reach fixation. It seems to be longer when S won, which makes
me worried this might be just drift for GR. I could run this for time to complete fixation, but it will take
about twice as long.

```{r}
f(p, "generation") + facet_wrap(periods ~ N, labeller = "label_both")
```


